Experiment 3 of 4

### 2018-08-11 experiments/D_exp_2/writeup/D_exp_2.Rmd
pretty coef D

```{r loadLibraries, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R'); library(Hmisc)
```

@@

```{r rtlmer, cache=TRUE}
rtlmer = lmerTest::lmer(data=rtdata,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
```

```{r rtlmersummaryxtable, results='asis', cache=TRUE, echo=F}
print(xtable(summary(rtlmer)$coef, digits=c(0,2,2,1,1,4)),type='html')
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
s1 <- subset(rtdata, subset=Selection=='Comparison')
s1lm <- lmerTest::lmer(data=s1, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s1lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
s2 <- subset(rtdata, subset=Selection=='Matching')
s2lm <- lmerTest::lmer(data=s2, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s2lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

>>>>

```{r loadLibraries, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R'); library(Hmisc)
library(broom)
library(broom.mixed)
source("add_stars.R")
library(kableExtra)
source("pretty_coef_table.R")
```

@@

```{r rtlmer, cache=TRUE, results='asis'}
dat_model <- rtdata
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtlmer = lmerTest::lmer(data=dat_model,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
pretty_coef_table(rtlmer, "rtlmer")
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
dat_model <- subset(rtdata, subset=Selection=='Comparison')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s1lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s1lm, "s1lm")
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
dat_model <- subset(rtdata, subset=Selection=='Matching')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s2lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s2lm, "s2lm")
```
